Between-dataset comparisons

### 2019-11-14 analysis/reports/cross_dataset.Rmd
add trendline

>>>>

Against nsamples

```{r nsamples}

skew_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = skew_percentile)) +
  geom_point(alpha = .1) +
    geom_smooth(method = "lm", se = F, color = "pink") +

  theme_bw() +
  ggtitle("Skew percentile v. nsamples")

skew_nsamples

simp_nsamples <- ggplot(data = filter(all_di, !singletons), aes(x = nsamples, y = simpson_percentile)) +
  geom_point(alpha = .1) + 
    geom_smooth(method = "lm", se = F, color = "pink") +

  theme_bw() +
  ggtitle("Simpson percentile v. nsamples")

simp_nsamples
```
